Timeliness of security updates for Android

### 2014-11-13 securityupdates.tex

@@

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Daniel R. Thomas,
Daniel T. Wagner,
Alastair R. Beresford,
Andrew Rice}
\IEEEauthorblockA{
Computer Laboratory\\
University of Cambridge\\
Cambridge, United Kingdom\\
Firstname.Lastname@cl.cam.ac.uk
}
}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{figures/proportioninsecure}
\caption{Proportion of devices running insecure, maybe insecure and secure versions of Android against time.
The red vertical lines are caused by vulnerabilities being discovered with those which have the biggest impact annotated.
This graph is explained further in XXX.}
\label{fig:proportioninsecure}
\end{figure}

@@

\section*{Acknowledgements}
Thanks to David Robertson for helpful advice on statistical analysis.
Thanks to Laurent Simon, Thomas Coudray, Adrian Taylor, Justin Case, Giant Pune and Khilan Gudka for reporting vulnerabilities in Android.

>>>>

% Blinding function
\newcommand{\identifying}[1]{#1}%{}
\newcommand{\blindauthors}[1]{#1}%{Paper \#59}%

@@

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\blindauthors{
\IEEEauthorblockN{Daniel R. Thomas,
Daniel T. Wagner,
Alastair R. Beresford,
Andrew Rice}
\IEEEauthorblockA{
Computer Laboratory\\
University of Cambridge\\
Cambridge, United Kingdom\\
Firstname.Lastname@cl.cam.ac.uk
}
}
}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{figures/proportioninsecure}
\caption{Proportion of devices running insecure, maybe insecure and secure versions of Android against time.
The red vertical lines are caused by vulnerabilities being discovered with those which have the biggest impact annotated.
%This graph is explained further in XXX.
}
\label{fig:proportioninsecure}
\end{figure}

@@

\identifying{
\section*{Acknowledgements}
Thanks to David Robertson for helpful advice on statistical analysis.
Thanks to Laurent Simon, Thomas Coudray, Adrian Taylor, Justin Case, Giant Pune and Khilan Gudka for reporting vulnerabilities in Android.
}
